---
title: "100 imputed datasets to Weka K = 7"
author: "Virginia_Ahedo"
date: "11/10/2020"
output: rmarkdown::github_document
---

#### Setup
#### Clean workspace
```{r setup, include=FALSE}
cat("\f")
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

#### Set working paths
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing")
dataPath <- "D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing"
```

#### Load required libraries
```{r}
require(mice)
require(dplyr)
require(varhandle)
require(RWeka)
```
#### Load Multiple Imputation (MICE) results
```{r}
imp_data_mice = readRDS("data_imp_MICE_def.Rda")
```

#### Load hierarchical clustering results for K = 7
```{r}
load("hc_7.Rda")
str(hc_7)
```

##### We transform hc_7$hc7.cluster into factor so that randomForest function assumes classification
```{r}
cluster = as.factor(hc_7$hc7.cluster)
```

#### Obtain the 100 datasets imputed with MICE and join each dataset with the result obtained from hc for K = 7.
##### Drop variables from EA001 to EA005, as after a conversation with the experts on the field, we agreed not to consider them in the RF analysis (they will be highly correlated with the cluster assignments). 
```{r}
for (k in 1:100){
  # Obtention of the imputed datasets
  imputedDataSet<-complete(imp_data_mice, k)
  not_for_RF = c("Gathering", "Hunting", "Fishing", "Husbandry", "Agriculture")
  imputedDataSet <- select(imputedDataSet, -all_of(not_for_RF))
  imputedDataSet = cbind(imputedDataSet, cluster)
  
  # Saving the imputed datasets as .arff
  arff_name = sprintf('MICE_imputed_df_K7_%s.arff', k)
  path <- "D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing/Multiple_Imputation_4_Weka_K7"
  write.arff(imputedDataSet, file.path(path, file = arff_name))
}
```

