---
title: "AOV & Duncan tests"
author: "Virginia_Ahedo"
date: "19/10/2020"
output: rmarkdown::github_document
---

#### Setup
#### Clean workspace
```{r setup, include=FALSE}
cat("\f")
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

#### Load required libraries
```{r}
require(xlsx)
require(agricolae)
require(tidyverse)
```

#### Load results experimenter K = 15, datasets = 1:50
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/Weka_experimenter")
results_k15_1_50 = read.csv("results_experimenter_classification_1_50.csv", header = T,
                            sep = ",", fileEncoding = "UTF-8")
```
#### Load results experimenter K = 15, datasets = 51:100
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/Weka_experimenter")
results_k15_51_100 = read.csv("results_experimenter_classification_test_Josema.csv", header = T,
                            sep = ",", fileEncoding = "UTF-8")
```
##### Check the structure of results_k15_1_50
```{r}
str(results_k15_1_50)
```
##### Check dimensions of results_k15_1_50
```{r}
dim(results_k15_1_50)
```
##### The dimensions obtained make sense since we have performed 10-fold CV on 50 datasets and applied 6 algorithms (6*x*10*50)

##### Check the structure of results_k15_51_100
```{r}
str(results_k15_51_100)
```
##### Check dimensions of results_k15_51_100
```{r}
dim(results_k15_51_100)
```
#### Extract the results
##### We begin with results_k15_1_50
##### 50 datasets * 10 folds = 500; 500 rows/algorithm * 6 algorithms = 3000
##### Beginning of each dataset in algorithm 1: 
```{r}
beg_1 = seq(1, 500, by = 10)
beg_1
```
##### Length of beg_1
```{r}
length(beg_1)
```
##### Number of folds
```{r}
n_folds = 10
```
##### Definition of necessary variables for k_1_50
```{r}
Accuracy_df_1_50 = data.frame(matrix(NA, nrow = 60, ncol = 50))
# nrow = 60: 6 algorithms * 10 folds/algorithm
# ncols = 50: 50 datasets
Algorithm_names = as.factor(c(rep("ZeroR", n_folds), rep("OneR", n_folds), rep("AdaBoost", n_folds),
                    rep("SVM_poly", n_folds), rep("RandomForest", n_folds), 
                    rep("RotationForest", n_folds)))
aov_pvalues_1_50 = as.numeric(rep(NA,50))
Duncan_df_1_50 = data.frame(matrix(NA, nrow = 6, ncol = 150))
RF_group_1_50 = as.character(rep(NA,50))
# nrow = 6 because we have 6 algorithms
# ncol = 150 because we keep algorithm name, accuracies and group (3 variables per dataset)
duncan_seq_ini = seq(1, 150, by = 3)
duncan_seq_end = seq(3, 150, by = 3)
```

##### Information retrieval
```{r}
for (i in 1:50){ #i selects the dataset
  alg_counter = 0
  for (j in seq(1, 60, by=10)){
    #j selects the index to access Accuracy_df_1_50 (10 rows for each algorithm)
    k_ini = beg_1[i] + 500*alg_counter #beginning of the folds for each algorithm
    k_end = k_ini + 9
    Accuracy_df_1_50[j:(j+9),i] = results_k15_1_50[k_ini:k_end,]$"Percent_correct"
    alg_counter = alg_counter + 1
  }
  # Test Anova
  anova_data_i = data.frame(as.numeric(Accuracy_df_1_50[,i]), Algorithm_names)
  colnames(anova_data_i) <- c("Percent_correct", "Algorithm")
  anova_test_i <- aov(anova_data_i$Percent_correct~anova_data_i$Algorithm, data = anova_data_i)
  aov_pvalues_1_50[i] <- summary(anova_test_i)[[1]][["Pr(>F)"]][1]
  
  # Multiple comparison test
  mult_comp_i <- duncan.test(anova_test_i, "anova_data_i$Algorithm", alpha = 0.05)
  Duncan_df_1_50[,duncan_seq_ini[i]:duncan_seq_end[i]] <- cbind(row.names(mult_comp_i$groups),
                                                       mult_comp_i$groups)
  RF_group_1_50[i] = as.character(mult_comp_i[[6]]["RandomForest","groups"])
}
```

#### Do the same now with results_k15_51_100
##### Definition of necessary variables for k_51_100
```{r}
Accuracy_df_51_100 = data.frame(matrix(NA, nrow = 60, ncol = 50))
# nrow = 60: 6 algorithms * 10 folds/algorithm
# ncols = 50: 50 datasets
Algorithm_names = as.factor(c(rep("ZeroR", n_folds), rep("OneR", n_folds), rep("AdaBoost", n_folds),
                    rep("SVM_poly", n_folds), rep("RandomForest", n_folds), 
                    rep("RotationForest", n_folds)))
aov_pvalues_51_100 = as.numeric(rep(NA,50))
Duncan_df_51_100 = data.frame(matrix(NA, nrow = 6, ncol = 150))
RF_group_51_100 = as.character(rep(NA,50))
# nrow = 6 because we have 6 algorithms
# ncol = 150 because we keep algorithm name, accuracies and group (3 variables per dataset)
duncan_seq_ini = seq(1, 150, by = 3)
duncan_seq_end = seq(3, 150, by = 3)
```

##### Information retrieval
```{r}
for (i in 1:50){ #i selects the dataset
  alg_counter = 0
  for (j in seq(1, 60, by=10)){
    #j selects the index to access Accuracy_df_1_50 (10 rows for each algorithm)
    k_ini = beg_1[i] + 500*alg_counter #beginning of the folds for each algorithm
    k_end = k_ini + 9
    Accuracy_df_51_100[j:(j+9),i] = results_k15_51_100[k_ini:k_end,]$"Percent_correct"
    alg_counter = alg_counter + 1
  }
  # Test Anova
  anova_data_i = data.frame(as.numeric(Accuracy_df_51_100[,i]), Algorithm_names)
  colnames(anova_data_i) <- c("Percent_correct", "Algorithm")
  anova_test_i <- aov(anova_data_i$Percent_correct~anova_data_i$Algorithm, data = anova_data_i)
  aov_pvalues_51_100[i] <- summary(anova_test_i)[[1]][["Pr(>F)"]][1]
  
  # Multiple comparison test
  mult_comp_i <- duncan.test(anova_test_i, "anova_data_i$Algorithm", alpha = 0.05)
  Duncan_df_51_100[,duncan_seq_ini[i]:duncan_seq_end[i]] <- cbind(row.names(mult_comp_i$groups),
                                                       mult_comp_i$groups)
  RF_group_51_100[i] = as.character(mult_comp_i[[6]]["RandomForest","groups"])
}
```
#### Join results 1_50 and 51_100
#### p_value
```{r}
aov_pvalues_1_100 = c(aov_pvalues_1_50, aov_pvalues_51_100)
```
##### Check that the AOV null hypothesis that the means of the different groups are the same can be rejected in all cases (p-value < 0.05)
```{r}
aov_pvalues_1_100 < 0.05
```
```{r}
sum(aov_pvalues_1_100 < 0.05)
```
#### Group to which RF belongs according to the Duncan test
```{r}
RF_group_1_100 = c(RF_group_1_50, RF_group_51_100)
RF_group_1_100
```
##### Check that in all cases RF group is "a"
##### If length(unique(x)) == 1, all values are equal
```{r}
length(unique(RF_group_1_100))
```
#### Detail of the Duncan test (joined)
```{r}
Duncan_df_1_100 = cbind(Duncan_df_1_50, Duncan_df_51_100)
dim(Duncan_df_1_100)
```
##### Save the detailed table of the 100 Duncan tests (one test per dataset)
```{r}
save(Duncan_df_1_100, file = "Detailed_Duncan_df_1_100.Rda")
write.csv(Duncan_df_1_100, "Detailed_Duncan_df_1_100.csv")
```

