---
title: "Consensus clustering"
author: "Virginia_Ahedo"
date: "8/10/2020"
output: rmarkdown::github_document
---
### Setup
### Clean workspace
```{r setup, include=FALSE}
cat("\f")
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

### Set working paths
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing")
dataPath <- "D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing"
```

### Load required libraries
```{r}
require(doParallel)
require(ConsensusClusterPlus)
require(dplyr)
```

### Configure parallel execution: 6 cores
```{r}
cl <- makeCluster(6)
registerDoParallel(cl)
```

### Loading input data. We are going to work with "Id_Clustering_db.Rda" since in ConsensusClusterPlus both rows and cols of the input matrix need to be named. Therefore, we will name our rows with the contents of "society_id"
```{r}
load("Id_Clustering_db.Rda")
```

#### Check the structure of "Id_Clustering_db.Rda"
```{r}
str(id_clust_db)
```
#### Clustering Analysis will be conducted on variables EA001 to EA005, thus, we drop column 7: Agriculture_intensity
#### In addition, we are going to drop "society_id" col, having previously saved its contents in a variable
```{r}
society_ids = id_clust_db$society_id
id_clust_db = select(id_clust_db, -c("society_id", "Agriculture_intensity"))
str(id_clust_db)
dim(id_clust_db)
```

### ConsensusClusterPlus input requirements:
#### - d: data matrix where columns=items/samples and rows are features
#### - After exploring the input matrix in the Tutorial, it appears that both rows and cols need to be named. We name here our rows with the contents of society_ids
```{r}
## Transform the id_clust_db dataframe into a matrix
final_clust_matrix = as.matrix(id_clust_db)

## Set society_ids as column names
rownames(final_clust_matrix) <- society_ids
str(final_clust_matrix)
```

#### Standardize elements in final_clust_matrix (substract the mean and divide by sd)
#### Such data transformation technique is widely used in clustering analysis.
##### The scale function, by default, centers and/or scales the COLUMNS of a numeric matrix. We want to scale EA001 to EA005, thus we scale prior to creating the transpose matrix.
```{r}
final_clust_matrix_norm = scale(final_clust_matrix)
str(final_clust_matrix_norm)
```

##### Drop attributes "scaled:center", "scaled:scale"
```{r}
attr(final_clust_matrix_norm,"scaled:center")<-NULL
attr(final_clust_matrix_norm,"scaled:scale")<-NULL
str(final_clust_matrix_norm)
```
#### To meet the input format requirements from ConsensusClusterPlus, we need to transpose our final_clust_matrix_norm
```{r}
## So as to have the items as columns, we need to transpose final_clust_matrix
t_final_clust_matrix_norm = t(final_clust_matrix_norm)
str(t_final_clust_matrix_norm)
dim(t_final_clust_matrix_norm)
```

### ConsensusClusterPlus function
```{r}
# Arguments:
# - d = data to be clustered. Data matrix where columns=items/samples and rows are features
# - maxK = integer value. Maximum cluster number to evaluate. In our case: 20.
#   The ConsensusClusterPlus Tutorial states: recommended cluster count: 20
# - reps = integer value. Number of subsamples. We set = 1000 as it is suggested in the Tutorial.
#   In his paper: Monti set reps to 500.
# - pItem = numerical value. Proportion of items to sample. We set pItem = 0.80 as Monti did.
# - pFeature = numerical value. Proportion of features to sample. We set pFeature = 1. (All features)
# - clusterAlg = character value. cluster algorithm. 'hc' hierarchical clustering (hclust).
# - title = character value for the output directory. 
# - innerLinkage = This option specifies the linkage method to use in iterative agglomerative hierarchical clustering. Not applicable to other clustering algorithms. We chose "ward.D2"
# - finalLinkage = This option specifies the linkage method to use in the final agglomerative hierarchical clustering. We chose "ward.D2".
# - distance = character value. 'pearson' (1 - Pearson correlation), 'spearman', 'euclidean', 'binary',...
#   In coherence with our previous analysis, we set distance = 'euclidean'
# - seed = optional numerical value. Sets random seed for reproducible results.
# - plot = NULL (print to screen), 'pdf', 'png'
# - writeTable = logical value. TRUE - write output and log to csv.
# - verbose = boolean. If TRUE, print messages to the screen to indicate progress.

title = "HC Euclidean Consensus Clustering"

rcc_Euclidean = ConsensusClusterPlus(d = t_final_clust_matrix_norm, maxK = 20, reps = 1000,
                                     pItem = 0.8, pFeature = 1, clusterAlg = 'hc',
                                     innerLinkage = "ward.D2", finalLinkage = "ward.D2",
                                     title = title, distance = 'euclidean', seed = 1, 
                                     plot = 'pdf', writeTable = T, verbose = F)
```

### Consensus Cluster and Consensus Item
```{r}
icl = calcICL(rcc_Euclidean, title = title, plot = "pdf", writeTable = T)

```

#### Check icl structure
```{r}
str(icl)
```

```{r}
str(icl$clusterConsensus)
```

#### Obtention of the mean value of cluster consensus for each K in Kmin:Kmax
##### Transform icl$clusterConsensus to dataframe
```{r}
clusterCons_data = as.data.frame(icl$clusterConsensus)
```

##### Attach so as to be able to call cols by name
```{r}
attach(clusterCons_data)
```

##### Variable definition
```{r}
Kmax = 20
consensus_mean <- data.frame(matrix(ncol = 2, nrow = (Kmax -1)))
names(consensus_mean) <- c("K", "Mean_cluster_consensus")

for (i in 1:(Kmax-1)){
  nb_clusters = i + 1
  consensus_mean[i,] <- c(nb_clusters, mean(clusterCons_data[clusterCons_data$k == nb_clusters,
                                                             "clusterConsensus"]))
}
```

##### Order consensus_mean
```{r}
consensus_mean[order(consensus_mean$Mean_cluster_consensus, decreasing = T),]
```
#### Save the results obtained
```{r}
save(rcc_Euclidean, file = "rcc_Euclidean_FINAL.Rda")
save(icl, file = "cluster_item_consensus.Rda")
save(consensus_mean, file = "consensusMean.Rda")
```