---
title: "Create MICE database"
author: "Virginia_Ahedo"
date: "10/10/2020"
output: rmarkdown::github_document
---

### Setup
### Clean workspace
```{r setup, include=FALSE}
cat("\f")
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

### Set working paths
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing")
dataPath <- "D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing"
```

### Load required libraries
```{r}
require(dplyr)
require(varhandle)
require(xlsx)
```

### Variables included in the MICE database
#### 1. Ethnographic Atlas (EA): Economy and subsistence
##### -EA001: % dependence on gathering
##### -EA002: % dependence on hunting
##### -EA003: % dependence on fishing
##### -EA004: % dependence on husbandry
##### -EA005: % dependence on agriculture
##### -EA028: Intensity of cultivation
##### -EA029: Major crop type
##### -EA030: Prevailing type settlement pattern
##### -EA033: Jurisdictional hierarchy beyond local community (Political complexity)
##### -EA039: Plow cultivation
##### -EA040: Domestic animals type
##### -EA041: Milking
##### -EA202: Population size

##### EA031: Mean size of local communities was not included due to the significant amount of missing data it had.

##### It is also important to note that in the supervised learning analysis we will not consider variables from EA001 to EA005, as the clustering analysis has been conducted exclusively on the five of them, and hence they are closely related to the output. 
##### However, for multiple imputation we DO consider variables EA001 to EA005 to help get more accurate estimates of the missing values.

#### 2. Variables from Jenkins et al. 2013:
##### - Amphibian Richness
##### - Bird Richness
##### - Mammal Richness
 
#### 3. Variables from Kreft and Jetz
##### - Vascular plants Richness

#### 4. Variables from Moderate Resolution Imaging Spectroradiometer
##### - Annual NPP Variance
##### - Monthly mean NPP
##### - NPP Constancy
##### - NPP Contingency
##### - NPP Predictability

#### 5. Variables from Terrestrial Ecoregions of the World
##### - Biome

#### 6. Variables from Baseline Historical ecoClimate model
##### - Annual Mean Temperature
##### - Annual Precipitation Variance
##### - Annual Temperature Variance
##### - Monthly Mean Precipitation
##### - Precipitation Constancy
##### - Precipitation Contingency
##### - Precipitation Predictability
##### - Temperature Constancy
##### - Temperature Contingency
##### - Temperature Predictability

### RAW DATA
#### 1. Ethnographic Atlas
```{r}
# Set the working directory to the corresponding subfolder within the current working directory
setwd(paste0(getwd(), "/Supervised Learning/EA"))
# 1. Ethnographic Atlas (EA):
# -EA001: % dependence on gathering
# -EA002: % dependence on hunting
# -EA003: % dependence on fishing
# -EA004: % dependence on husbandry
# -EA005: % dependence on agriculture
# -EA028: Intensity of cultivation --> NUMERICAL
# -EA029: Major crop type --> NUMERICAL
# -EA030: Prevailing type settlement pattern --> NUMERICAL
# -EA033: Jurisdictional hierarchy beyond local community (Political complexity) --> NUMERICAL
# -EA039: Plow cultivation --> NUMERICAL
# -EA040: Domestic animals type --> CATEGORICAL
# -EA041: Milking --> CATEGORICAL
# -EA202: Population size

EA001 = read.csv("EA001.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA002 = read.csv("EA002.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA003 = read.csv("EA003.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA004 = read.csv("EA004.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA005 = read.csv("EA005.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA028 = read.csv("EA028.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA029 = read.csv("EA029.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA030 = read.csv("EA030.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA033 = read.csv("EA033.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA039 = read.csv("EA039.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA040 = read.csv("EA040.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA041 = read.csv("EA041.csv", header = T, sep = ",", fileEncoding = "UTF-8")
EA202 = read.csv("EA202.csv", header = T, sep = ",", fileEncoding = "UTF-8")
```
##### Check EA dimensionality coherence
```{r}
cat("Dimensions of dataset EA001: ", dim(EA001))
cat("\nDimensions of dataset EA002: ", dim(EA002))
cat("\nDimensions of dataset EA003: ", dim(EA003))
cat("\nDimensions of dataset EA004: ", dim(EA004))
cat("\nDimensions of dataset EA005: ", dim(EA005))
cat("\nDimensions of dataset EA028: ", dim(EA028))
cat("\nDimensions of dataset EA029: ", dim(EA029))
cat("\nDimensions of dataset EA030: ", dim(EA030))
cat("\nDimensions of dataset EA033: ", dim(EA033))
cat("\nDimensions of dataset EA039: ", dim(EA039))
cat("\nDimensions of dataset EA040: ", dim(EA040))
cat("\nDimensions of dataset EA041: ", dim(EA041))
cat("\nDimensions of dataset EA202: ", dim(EA202))
```
#### Drop unnecessary columns before building the unified db
##### For ordinal variables, we will keep the data in the code column and set it as.numeric()
```{r}
#Columns to drop in the variables that are NUMERICAL
num_vars_cols2drop = c("society_name", "society_xd_id", "language_glottocode", "language_name",
                       "language_family","variable_id", "code_label", "focal_year", "sub_case",
                       "comment")

#Columns to drop in the variables that are CATEGORICAL
cat_vars_cols2drop = c("society_name", "society_xd_id", "language_glottocode", "language_name",
                       "language_family","variable_id", "code", "focal_year", "sub_case", "comment")
```
##### Preprocessing of EA NUMERICAL VARIABLES
```{r}
# Percentage of dependence on different subsistence economies
EA001_s <- unfactor(select(EA001, -all_of(num_vars_cols2drop)))
names(EA001_s)[names(EA001_s) == "code"] <- "Gathering"

EA002_s <- unfactor(select(EA002, -all_of(num_vars_cols2drop)))
names(EA002_s)[names(EA002_s) == "code"] <- "Hunting"

EA003_s <- unfactor(select(EA003, -all_of(num_vars_cols2drop)))
names(EA003_s)[names(EA003_s) == "code"] <- "Fishing"

EA004_s <- unfactor(select(EA004, -all_of(num_vars_cols2drop)))
names(EA004_s)[names(EA004_s) == "code"] <- "Husbandry"

EA005_s <- unfactor(select(EA005, -all_of(num_vars_cols2drop)))
names(EA005_s)[names(EA005_s) == "code"] <- "Agriculture"

# Agriculture-related variables: EA028, EA029, EA039
# Variables from EA028 to EA039 have been considered as NUMERICAL CONTINUOUS variables
# in order not to lose information about order. Consequently, we have dropped code_label col,
# which is a factor (char)

EA028_s <- unfactor(select(EA028, -all_of(num_vars_cols2drop)))
names(EA028_s)[names(EA028_s) == "code"] <- "Agriculture_intensity"

EA029_s <- unfactor(select(EA029, -all_of(num_vars_cols2drop)))
names(EA029_s)[names(EA029_s) == "code"] <- "Major_crop_type"

EA039_s <- unfactor(select(EA039, -all_of(num_vars_cols2drop)))
names(EA039_s)[names(EA039_s) == "code"] <- "Plow_cultivation"

# EA Variables considered independently

# EA030: Prevailing type settlement pattern --> NUMERICAL
EA030_s <- unfactor(select(EA030, -all_of(num_vars_cols2drop)))
names(EA030_s)[names(EA030_s) == "code"] <- "Settlement_pattern"

# EA033: Political complexity --> NUMERICAL
EA033_s <- unfactor(select(EA033, -all_of(num_vars_cols2drop)))
names(EA033_s)[names(EA033_s) == "code"] <- "Political_complexity"

# EA202: Population size. Considered numerical & continuous 
EA202_s <- unfactor(select(EA202, -all_of(num_vars_cols2drop)))
names(EA202_s)[names(EA202_s) == "code"] <- "Population_size"
```
##### Preprocessing of EA CATEGORICAL variables
```{r}
# EA040: Domestic animals type: considered as FACTOR
EA040_s <- select(EA040, -all_of(cat_vars_cols2drop))
names(EA040_s)[names(EA040_s) == "code_label"] <- "Animal_type"
EA040_s$society_id <- as.character(EA040_s$society_id)

# EA041: Milking: considered as FACTOR
EA041_s <- select(EA041, -all_of(cat_vars_cols2drop))
names(EA041_s)[names(EA041_s) == "code_label"] <- "Milking"
EA041_s$society_id <- as.character(EA041_s$society_id)
```
##### Build unified_EA_db: Include attribute all = T, so that it does not drop registers with NAs
```{r}
## Inclusion of all = T
EA_unified_01 = merge(EA001_s, EA002_s, by.x="society_id", all = T)
EA_unified_02 = merge(EA_unified_01, EA003_s, by.x="society_id", all = T)
EA_unified_03 = merge(EA_unified_02, EA004_s, by.x="society_id", all = T)
EA_unified_04 = merge(EA_unified_03, EA005_s, by.x="society_id", all = T)
EA_unified_05 = merge(EA_unified_04, EA028_s, by.x="society_id", all = T)
EA_unified_06 = merge(EA_unified_05, EA029_s, by.x="society_id", all = T)
EA_unified_07 = merge(EA_unified_06, EA030_s, by.x="society_id", all = T)
EA_unified_08 = merge(EA_unified_07, EA033_s, by.x="society_id", all = T)
EA_unified_09 = merge(EA_unified_08, EA039_s, by.x="society_id", all = T)
EA_unified_10 = merge(EA_unified_09, EA040_s, by.x="society_id", all = T)
EA_unified_11 = merge(EA_unified_10, EA041_s, by.x="society_id", all = T)
EA_unified_12 = merge(EA_unified_11, EA202_s, by.x="society_id", all = T)
```
#### 2. Variables from Jenkins et al. 2013: all these varibles are NUMERICAL
```{r}
# Set the working directory to the corresponding subfolder within the current working directory
setwd(paste0(getwd(), "/Supervised Learning/Jenkins"))
# 2. Variables from Jenkins et al. 2013:
# - Amphibian Richness
# - Bird Richness
# - Mammal Richness
Amphibians = read.csv("AmphibianRichness.csv", header = T, sep = ",", fileEncoding = "UTF-8")
Birds = read.csv("BirdRichness.csv", header = T, sep = ",", fileEncoding = "UTF-8")
Mammals = read.csv("MammalRichness.csv", header = T, sep = ",", fileEncoding = "UTF-8")
```
##### Check Jenkins et al. 2013 dimensionality coherence
```{r}
cat("Dimensions of dataset Amphibians: ", dim(Amphibians))
cat("\nDimensions of dataset Birds: ", dim(Birds))
cat("\nDimensions of dataset Mammals: ", dim(Mammals))
```
##### Drop unnecessary columns from Jenkins et al.
##### Check structure
```{r}
str(Amphibians)
```
##### The columns to drop are the same as in the EA numeric variables
```{r}
Amphibians_s <- unfactor(select(Amphibians, -all_of(num_vars_cols2drop)))
names(Amphibians_s)[names(Amphibians_s) == "code"] <- "Amphibian_richness"

Birds_s <- unfactor(select(Birds, -all_of(num_vars_cols2drop)))
names(Birds_s)[names(Birds_s) == "code"] <- "Bird_richness"

Mammals_s <- unfactor(select(Mammals, -all_of(num_vars_cols2drop)))
names(Mammals_s)[names(Mammals_s) == "code"] <- "Mammal_richness"
```
##### Check how many of our societies from EA are included in Jenkins
```{r}
sum(EA_unified_12$society_id %in% Amphibians_s$society_id)
sum(EA_unified_12$society_id %in% Birds_s$society_id)
sum(EA_unified_12$society_id %in% Mammals_s$society_id)
```
##### Merge EA and variables from Jenkins et al. 2013:
##### Left join
```{r}
EA_Jenkins_01 = merge(EA_unified_12, Amphibians_s, by = "society_id", all.x = T)
EA_Jenkins_02 = merge(EA_Jenkins_01, Birds_s, by = "society_id", all.x = T)
EA_Jenkins_03 = merge(EA_Jenkins_02, Mammals_s, by = "society_id", all.x = T)
```
#### 3. Variables from Kreft and Jetz: NUMERICAL
```{r}
# Set the working directory to the corresponding subfolder within the current working directory
setwd(paste0(getwd(), "/Supervised Learning/Kreft and Jetz"))
# 3. Variables from Kreft and Jetz
# - Vascular plants Richness
Vascular_plants = read.csv("VascularPlantsRichness.csv", header = T, sep = ",", fileEncoding = "UTF-8")
```
##### Check dimensions
```{r}
cat("Dimensions of dataset VascularPlants: ", dim(Vascular_plants))
```
##### Drop unnecessary columns from Kreft and Jetz
##### Check structure
```{r}
str(Vascular_plants)
```
##### The columns to drop are the same as in the EA numeric variables
```{r}
Vascular_plants_s <- unfactor(select(Vascular_plants, -all_of(num_vars_cols2drop)))
names(Vascular_plants_s)[names(Vascular_plants_s) == "code"] <- "Plants_richness"
```

##### Merge with EA_Jenkins_03
##### Left join
```{r}
EA_Kreft = merge(EA_Jenkins_03, Vascular_plants_s, by = "society_id", all.x = T)
```

#### 4. Variables from Moderate Resolution Imaging Spectroradiometer: NUMERICAL
```{r}
# Set the working directory to the corresponding subfolder within the current working directory
setwd(paste0(getwd(), "/Supervised Learning/Spectroradiometer"))
# 4. Variables from Moderate Resolution Imaging Spectroradiometer
# - Annual NPP Variance
# - Monthly mean NPP
# - NPP Constancy
# - NPP Contingency
# - NPP Predictability

Annual_NPP_Var = read.csv("AnnualNetPrimaryProductionVariance.csv", header = T, sep = ",", 
                          fileEncoding = "UTF-8")
Monthly_mean_NPP = read.csv("MonthlyMeanNetPrimaryProduction.csv", header = T, sep = ",", 
                            fileEncoding = "UTF-8")
NPP_Constancy = read.csv("NetPrimaryProductionConstancy.csv", header = T, sep = ",", 
                         fileEncoding = "UTF-8")
NPP_Contingency = read.csv("NetPrimaryProductionContingency.csv", header = T, sep = ",", 
                           fileEncoding = "UTF-8")
NPP_Predictability = read.csv("NetPrimaryProductionPredictability.csv", header = T, sep = ",",
                              fileEncoding = "UTF-8")
```
##### Check Moderate Resolution Imaging Spectroradiometer dimensionality coherence
```{r}
cat("Dimensions of dataset Annual_NPP_Variance: ", dim(Annual_NPP_Var))
cat("\nDimensions of dataset Monthly_mean_NPP: ", dim(Monthly_mean_NPP))
cat("\nDimensions of dataset NPP_Constancy: ", dim(NPP_Constancy))
cat("\nDimensions of dataset NPP_Contingency: ", dim(NPP_Contingency))
cat("\nDimensions of dataset NPP_Predictability: ", dim(NPP_Predictability))
```
##### Drop unnecessary columns from Resolution Imaging Spectroradiometer variables
##### Check structure
```{r}
str(Annual_NPP_Var)
```
##### The columns to drop are the same as in the EA numeric variables
```{r}
Annual_NPP_Var_s <- unfactor(select(Annual_NPP_Var, -all_of(num_vars_cols2drop)))
names(Annual_NPP_Var_s)[names(Annual_NPP_Var_s) == "code"] <- "Annual_NPP_Var"

Monthly_mean_NPP_s <- unfactor(select(Monthly_mean_NPP, -all_of(num_vars_cols2drop)))
names(Monthly_mean_NPP_s)[names(Monthly_mean_NPP_s) == "code"] <- "Monthly_mean_NPP"

NPP_Constancy_s <- unfactor(select(NPP_Constancy, -all_of(num_vars_cols2drop)))
names(NPP_Constancy_s)[names(NPP_Constancy_s) == "code"] <- "NPP_Constancy"

NPP_Contingency_s <- unfactor(select(NPP_Contingency, -all_of(num_vars_cols2drop)))
names(NPP_Contingency_s)[names(NPP_Contingency_s) == "code"] <- "NPP_Contingency"

NPP_Predictability_s <- unfactor(select(NPP_Predictability, -all_of(num_vars_cols2drop)))
names(NPP_Predictability_s)[names(NPP_Predictability_s) == "code"] <- "NPP_Predictability"
```
##### Merge variables from Resolution Imaging Spectroradiometer
##### Left join
```{r}
EA_RIS_01 = merge(EA_Kreft, Annual_NPP_Var_s, by = "society_id", all.x = T)
EA_RIS_02 = merge(EA_RIS_01, Monthly_mean_NPP_s, by = "society_id", all.x = T)
EA_RIS_03 = merge(EA_RIS_02, NPP_Constancy_s, by = "society_id", all.x = T)
EA_RIS_04 = merge(EA_RIS_03, NPP_Contingency_s, by = "society_id", all.x = T)
EA_RIS_05 = merge(EA_RIS_04, NPP_Predictability_s, by = "society_id", all.x = T)
```
#### 5. Variables from Terrestrial Ecoregions of the World
```{r}
# Set the working directory to the corresponding subfolder within the current working directory
setwd(paste0(getwd(), "/Supervised Learning/EcoRegions"))
# 5. Variables from Terrestrial Ecoregions of the World
# - Biome
Biome = read.csv("Biome.csv", header = T, sep = ",", fileEncoding = "UTF-8")
```
##### Check Biome dimensions
```{r}
cat("Dimensions of Biome: ", dim(Biome))
```
##### Drop unnecessary columns from Biome
##### Check structure
```{r}
str(Biome)
```
##### This variable is a FACTOR, we keep code_label and drop the same cols. as in the EA categorical variables
```{r}
Biome_s <- select(Biome, -all_of(cat_vars_cols2drop))
names(Biome_s)[names(Biome_s) == "code_label"] <- "Biome"
Biome_s$society_id <- as.character(Biome_s$society_id)
```
##### Merge with EA_RIS_05
##### Left join
```{r}
EA_Biome = merge(EA_RIS_05, Biome_s, by = "society_id", all.x = T)
```
#### 6. Variables from Baseline Historical ecoClimate model: NUMERICAL
```{r}
# Set the working directory to the corresponding subfolder within the current working directory
setwd(paste0(getwd(), "/Supervised Learning/EcoClimate"))
# 6. Variables from Baseline Historical ecoClimate model
# - Annual Mean Temperature
# - Annual Precipitation Variance
# - Annual Temperature Variance
# - Monthly Mean Precipitation
# - Precipitation Constancy
# - Precipitation Contingency
# - Precipitation Predictability
# - Temperature Constancy
# - Temperature Contingency
# - Temperature Predictability

Annual_Mean_Temp = read.csv("AnnualMeanTemperature.csv", header = T, sep = ",", fileEncoding = "UTF-8")
Annual_Precip_Var = read.csv("AnnualPrecipitationVariance.csv", header = T, sep = ",")
Annual_Temp_Var = read.csv("AnnualTemperatureVariance.csv", header = T, sep = ",")
Monthly_Mean_Precip = read.csv("MonthlyMeanPrecipitation.csv", header = T, sep = ",")
Precip_Constancy = read.csv("PrecipitationConstancy.csv", header = T, sep = ",")
Precip_Contingency = read.csv("PrecipitationContingency.csv", header = T, sep = ",")
Precip_Predictability = read.csv("PrecipitationPredictability.csv", header = T, sep = ",")
Temp_Constancy = read.csv("TemperatureConstancy.csv", header = T, sep = ",")
Temp_Contingency = read.csv("TemperatureContingency.csv", header = T, sep = ",")
Temp_Predictability = read.csv("TemperaturePredictability.csv", header = T, sep = ",")
```
##### Check Baseline Historical ecoClimate model variables dimensionality coherence
```{r}
cat("Dimensions of dataset Annual_Mean_Temp: ", dim(Annual_Mean_Temp))
cat("\nDimensions of dataset Annual_Precip_Var: ", dim(Annual_Precip_Var))
cat("\nDimensions of dataset Annual_Temp_Var: ", dim(Annual_Temp_Var))
cat("\nDimensions of dataset Monthly_Mean_Precip: ", dim(Monthly_Mean_Precip))
cat("\nDimensions of dataset Precip_Constancy: ", dim(Precip_Constancy))
cat("\nDimensions of dataset Precip_Contingency: ", dim(Precip_Contingency))
cat("\nDimensions of dataset Precip_Predictability: ", dim(Precip_Predictability))
cat("\nDimensions of dataset Temp_Constancy: ", dim(Temp_Constancy))
cat("\nDimensions of dataset Temp_Contingency: ", dim(Temp_Contingency))
cat("\nDimensions of dataset Temp_Predictability: ", dim(Temp_Predictability))
```
##### Drop unnecessary columns from BH ecoClimate model
##### Check structure
```{r}
str(Annual_Mean_Temp)
```
##### The columns to drop are the same as in the EA numeric variables
```{r}
Annual_Mean_Temp_s <- unfactor(select(Annual_Mean_Temp, -all_of(num_vars_cols2drop)))
names(Annual_Mean_Temp_s)[names(Annual_Mean_Temp_s) == "code"] <- "Annual_Mean_Temp"

Annual_Precip_Var_s <- unfactor(select(Annual_Precip_Var, -all_of(num_vars_cols2drop)))
names(Annual_Precip_Var_s)[names(Annual_Precip_Var_s) == "code"] <- "Annual_Precip_Var"

Annual_Temp_Var_s <- unfactor(select(Annual_Temp_Var, -all_of(num_vars_cols2drop)))
names(Annual_Temp_Var_s)[names(Annual_Temp_Var_s) == "code"] <- "Annual_Temp_Var"

Monthly_Mean_Precip_s <- unfactor(select(Monthly_Mean_Precip, -all_of(num_vars_cols2drop)))
names(Monthly_Mean_Precip_s)[names(Monthly_Mean_Precip_s) == "code"] <- "Monthly_Mean_Precip"

Precip_Constancy_s <- unfactor(select(Precip_Constancy, -all_of(num_vars_cols2drop)))
names(Precip_Constancy_s)[names(Precip_Constancy_s) == "code"] <- "Precip_Constancy"

Precip_Contingency_s <- unfactor(select(Precip_Contingency, -all_of(num_vars_cols2drop)))
names(Precip_Contingency_s)[names(Precip_Contingency_s) == "code"] <- "Precip_Contingency"

Precip_Predictability_s <- unfactor(select(Precip_Predictability, -all_of(num_vars_cols2drop)))
names(Precip_Predictability_s)[names(Precip_Predictability_s) == "code"] <- "Precip_Predictability"

Temp_Constancy_s <- unfactor(select(Temp_Constancy, -all_of(num_vars_cols2drop)))
names(Temp_Constancy_s)[names(Temp_Constancy_s) == "code"] <- "Temp_Constancy"

Temp_Contingency_s <- unfactor(select(Temp_Contingency, -all_of(num_vars_cols2drop)))
names(Temp_Contingency_s)[names(Temp_Contingency_s) == "code"] <- "Temp_Contingency"

Temp_Predictability_s <- unfactor(select(Temp_Predictability, -all_of(num_vars_cols2drop)))
names(Temp_Predictability_s)[names(Temp_Predictability_s) == "code"] <- "Temp_Predictability"
```
##### Merge with EA_Biome
##### Left join
```{r}
EA_ecoClimate_01 = merge(EA_Biome, Annual_Mean_Temp_s, by = "society_id", all.x = T)
EA_ecoClimate_02 = merge(EA_ecoClimate_01, Annual_Precip_Var_s, by = "society_id", all.x = T)
EA_ecoClimate_03 = merge(EA_ecoClimate_02, Annual_Temp_Var_s, by = "society_id", all.x = T)
EA_ecoClimate_04 = merge(EA_ecoClimate_03, Monthly_Mean_Precip_s, by = "society_id", all.x = T)
EA_ecoClimate_05 = merge(EA_ecoClimate_04, Precip_Constancy_s, by = "society_id", all.x = T)
EA_ecoClimate_06 = merge(EA_ecoClimate_05, Precip_Contingency_s, by = "society_id", all.x = T)
EA_ecoClimate_07 = merge(EA_ecoClimate_06, Precip_Predictability_s, by = "society_id", all.x = T)
EA_ecoClimate_08 = merge(EA_ecoClimate_07, Temp_Constancy_s, by = "society_id", all.x = T)
EA_ecoClimate_09 = merge(EA_ecoClimate_08, Temp_Contingency_s, by = "society_id", all.x = T)
EA_ecoClimate_final = merge(EA_ecoClimate_09, Temp_Predictability_s, by = "society_id", all.x = T)
```
## Save MICE database
```{r}
save(EA_ecoClimate_final, file = "Database_for_MICE.Rda")
write.csv(EA_ecoClimate_final, file = "Database_for_MICE.csv")
```