---
title: "Multiple imputation MICE"
author: "Virginia_Ahedo"
date: "11/10/2020"
output: rmarkdown::github_document
---

#### Setup
#### Clean workspace
```{r setup, include=FALSE}
cat("\f")
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

#### Set working paths
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing")
dataPath <- "D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing"
```

#### Parallel execution: 6 cores
```{r}
require(doParallel)
cl <- makeCluster(12)
registerDoParallel(cl)
```

#### Load "Database_for_MICE.Rda"
```{r}
load("Database_for_MICE.Rda")
```

##### Check the dimensions of EA_ecoClimate_final
```{r}
dim(EA_ecoClimate_final)
names(EA_ecoClimate_final)
```
##### Load "Named_Clustering_db.Rda", to make sure that in the Supervised Learning approach we are working with exactly the same societies as in the Clustering Analysis section.
```{r}
load("Named_Clustering_db.Rda")
dim(named_clust_db)
names(named_clust_db)
```
##### Find out which is the society that makes the difference between EA_ecoClimate_final and named_clust_db
```{r}
which(EA_ecoClimate_final$society_id %in% named_clust_db$society_id == FALSE)
```
```{r}
EA_ecoClimate_final[1125, ]
```
##### Drop row 1125 from EA_ecoClimate_final
```{r}
data = EA_ecoClimate_final[-1125,]
str(data)
```

### MULTIPLE IMPUTATION
#### Preliminary Analysis with VIM 
```{r}
library(VIM)
data_plot <- aggr(data, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(data), cex.axis=.7,
                    gap=3, ylab=c("Missing data","Pattern"))

```

#### Preliminary analysis with naniar
```{r}
library(naniar)
naniar::gg_miss_var(data)
```

#### Preliminary analysis with VIM (restricted to variables with NAs)
```{r}

subsetdataWithNA<-data[,colSums(is.na.data.frame(data))>0]

data_plot <- aggr(subsetdataWithNA, col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(subsetdataWithNA), cex.axis=.45,cex.numbers = 0.7,
                    gap=3, ylab=c("Missing data","Pattern"))

```

#### Preliminary analysis witn naniar (restricted to variables with NAs)
```{r}
library(naniar)
naniar::gg_miss_var(subsetdataWithNA)
```
##### Additional visualizations
```{r}
# https://cran.r-project.org/web/packages/naniar/vignettes/getting-started-w-naniar.html
library(visdat)
vis_dat(data)
```
```{r}
vis_miss(data)
```
### Data imputation with MICE
#### MICE is the most suitable tool for MULTIPLE IMPUTATION
```{r}
library(mice)
```

##### Drop society_id from data before performing the data imputation with MICE
```{r}
require(dplyr)
data_final = select(data, -c("society_id"))
str(data_final)
```

```{r}
data_imp_MICE <-mice(data=data_final, m=100,maxit=50,method='rf', remove.collinear = FALSE,seed=27)
saveRDS(data_imp_MICE, file="data_imp_MICE_def.Rda")
```

