---
title: "Stacked bar charts"
author: "Virginia_Ahedo"
date: "16/10/2020"
output: rmarkdown::github_document
---

#### Setup
#### Clean workspace
```{r setup, include=FALSE}
cat("\f")
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

#### Set working paths
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing")
dataPath <- "D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing"
```

#### Load required libraries
```{r}
require(dplyr)
require(DescTools) #Necessary for mode calculation

## Libraries necessary for the plots
require(ggplot2)
```

#### Load hc_interpretation.Rda files
```{r}
load("hc2_interpretation.Rda")
load("hc7_interpretation.Rda")
load("hc15_interpretation.Rda")
```

#### Preprocessing the interpretation files
##### Select just columns from EA001 to EA005 and hcx.cluster
```{r}
names(hc2_interpretation)
```
##### Create variable cols_2_drop
```{r}
cols_2_drop = c("society_id", "society_name", "Agriculture_intensity", "major_crop_type",
                "settlement_patterns", "mean_size_communities", "plow", "domestic_animals",
                "milking", "population_size")
```
##### Drop the above-selected columns from the hcx_interpretation dataframes.
```{r}
hc2_interpretation_s <- select(hc2_interpretation, -all_of(cols_2_drop))
hc7_interpretation_s <- select(hc7_interpretation, -all_of(cols_2_drop))
hc15_interpretation_s <- select(hc15_interpretation, -all_of(cols_2_drop))
```
#### Check that the sum from cols EA001 to EA005 is 100.
##### hc_2
```{r}
EA001_005_sum_hc2 = rowSums(hc2_interpretation_s[,1:5])
EA001_005_sum_hc2
```
##### hc_7
```{r}
EA001_005_sum_hc7 = rowSums(hc7_interpretation_s[,1:5])
EA001_005_sum_hc7
```
##### hc_15
```{r}
EA001_005_sum_hc15 = rowSums(hc15_interpretation_s[,1:5])
EA001_005_sum_hc15
```
#### Obtention of different statistics for each k = 2, 7, 15.
##### The statistics to calculate are: colMeans, std, median, mode.
#### K = 2
```{r}
for (k in 1:2){
  
  #Mean
  assign(paste("hc2_colMeans_k_", k, sep = ""),
         colMeans(hc2_interpretation_s[hc2_interpretation_s$hc2.cluster == k, 1:5]))
  
  #Standard deviation
  assign(paste("hc2_sd_k_", k, sep = ""),
         apply(hc2_interpretation_s[hc2_interpretation_s$hc2.cluster == k, 1:5], 2, sd))
  
  #Median
  assign(paste("hc2_median_k_", k, sep = ""),
         apply(hc2_interpretation_s[hc2_interpretation_s$hc2.cluster == k, 1:5], 2, median))
  
  #Mode
  assign(paste("hc2_mode_k_", k, sep = ""),
         apply(hc2_interpretation_s[hc2_interpretation_s$hc2.cluster == k, 1:5], 2, Mode))
  
  #Create a dataframe with all the statistics for each cluster
  assign(paste("hc2_statistics_k_", k, sep = ""),
         rbind(get(paste0("hc2_colMeans_k_", k)), get(paste0("hc2_median_k_", k)), 
               get(paste0("hc2_mode_k_", k)), get(paste0("hc2_sd_k_", k))))
  #Include column with cluster_id
  clust_id = rep(paste("c", k, sep = ""), 4)
  labelling <- cbind(get(paste0("hc2_statistics_k_", k)), clust_id)
  rownames(labelling) <- c("Mean", "Median", "Mode", "SD")
  assign(paste("hc2_statistics_k_", k, sep = ""), data.frame(labelling))
}
```

#### K = 7
```{r}
for (l in 1:7){
  
  #Mean
  assign(paste("hc7_colMeans_k_", l, sep = ""),
         colMeans(hc7_interpretation_s[hc7_interpretation_s$hc7.cluster == l, 1:5]))
  
  #Standard deviation
  assign(paste("hc7_sd_k_", l, sep = ""),
         apply(hc7_interpretation_s[hc7_interpretation_s$hc7.cluster == l, 1:5], 2, sd))
  
  #Median
  assign(paste("hc7_median_k_", l, sep = ""),
         apply(hc7_interpretation_s[hc7_interpretation_s$hc7.cluster  == l, 1:5], 2, median))
  
  #Mode
  assign(paste("hc7_mode_k_", l, sep = ""),
         apply(hc7_interpretation_s[hc7_interpretation_s$hc7.cluster == l, 1:5], 2, Mode))
  
  #Create a dataframe with all the statistics for each cluster
  assign(paste("hc7_statistics_k_", l, sep = ""),
         rbind(get(paste0("hc7_colMeans_k_", l)), get(paste0("hc7_median_k_", l)), 
               get(paste0("hc7_mode_k_", l)), get(paste0("hc7_sd_k_", l))))
  clust_id = rep(paste("c", l, sep = ""), 4)
  labelling <- cbind(get(paste0("hc7_statistics_k_", l)), clust_id)
  rownames(labelling) <- c("Mean", "Median", "Mode", "SD")
  assign(paste("hc7_statistics_k_", l, sep = ""), data.frame(labelling))  
}
```

#### K = 15
```{r}
for (m in 1:15){
  
  #Mean
  assign(paste("hc15_colMeans_k_", m, sep = ""),
         colMeans(hc15_interpretation_s[hc15_interpretation_s$hc15.cluster == m, 1:5]))
  
  #Standard deviation
  assign(paste("hc15_sd_k_", m, sep = ""),
         apply(hc15_interpretation_s[hc15_interpretation_s$hc15.cluster == m, 1:5], 2, sd))
  
  #Median
  assign(paste("hc15_median_k_", m, sep = ""),
         apply(hc15_interpretation_s[hc15_interpretation_s$hc15.cluster == m, 1:5], 2, median))
  
  #Mode
  assign(paste("hc15_mode_k_", m, sep = ""), 
         apply(hc15_interpretation_s[hc15_interpretation_s$hc15.cluster == m, 1:5], 2, Mode))
  
  #Create a dataframe with all the statistics for each cluster
  assign(paste("hc15_statistics_k_", m, sep = ""),
         rbind(get(paste0("hc15_colMeans_k_", m)), get(paste0("hc15_median_k_", m)), 
               get(paste0("hc15_mode_k_", m)), get(paste0("hc15_sd_k_", m))))
  clust_id = rep(paste("c", m, sep = ""), 4)
  labelling <- cbind(get(paste0("hc15_statistics_k_", m)), clust_id)
  rownames(labelling) <- c("Mean", "Median", "Mode", "SD")
  assign(paste("hc15_statistics_k_", m, sep = ""), data.frame(labelling))    
}
```

#### Plots of the average values for the different Ks.
##### Fist step: for each K, rowBind the mean values of each cluster in a dataframe.
##### Second step: for each K, rowBind the sd of each cluster in a dataframe

#### K = 2
##### Mean values dataframe
```{r}
mean_df_2 <- data.frame()
sd_df_2 <- data.frame()
for (i in 1:2){
  mean_df_2 = rbind(mean_df_2, get(paste0("hc2_colMeans_k_", i)))
  sd_df_2 = rbind(sd_df_2, get(paste0("hc2_sd_k_", i)))
}

# Name rows and cols from mean_df_2 and sd_df_2
colnames(mean_df_2) <- names(hc2_colMeans_k_1)
rownames(mean_df_2) <- c("c1", "c2")
colnames(sd_df_2) <- names(hc2_colMeans_k_1)
rownames(sd_df_2) <- c("c1", "c2")
```

#### K = 7
##### Mean values dataframe
```{r}
mean_df_7 <- data.frame()
sd_df_7 <- data.frame()
for (j in 1:7){
  mean_df_7 = rbind(mean_df_7, get(paste0("hc7_colMeans_k_", j)))
  sd_df_7 = rbind(sd_df_7, get(paste0("hc7_sd_k_", j)))
}

# Name rows and cols from mean_df_7 and sd_df_7
colnames(mean_df_7) <- names(hc7_colMeans_k_1)
rownames(mean_df_7) <- c("c1", "c2", "c3", "c4", "c5", "c6", "c7")
colnames(sd_df_7) <- names(hc7_colMeans_k_1)
rownames(sd_df_7) <- c("c1", "c2", "c3", "c4", "c5", "c6", "c7")
```

#### K = 15
##### Mean values dataframe
```{r}
mean_df_15 <- data.frame()
sd_df_15 <- data.frame()
for (k in 1:15){
  mean_df_15 = rbind(mean_df_15, get(paste0("hc15_colMeans_k_", k)))
  sd_df_15 = rbind(sd_df_15, get(paste0("hc15_sd_k_", k)))
}

# Name rows and cols from mean_df_15 and sd_df_15
colnames(mean_df_15) <- names(hc15_colMeans_k_1)
rownames(mean_df_15) <- c("c1", "c2", "c3", "c4", "c5", "c6", "c7", "c8",
                          "c9", "c10", "c11", "c12", "c13", "c14", "c15")
colnames(sd_df_15) <- names(hc15_colMeans_k_1)
rownames(sd_df_15) <- c("c1", "c2", "c3", "c4", "c5", "c6", "c7", "c8",
                        "c9", "c10", "c11", "c12", "c13", "c14", "c15")
```

### Percentage stacked bar charts for each K
##### https://community.rstudio.com/t/create-a-percentage-stacked-bar-chart/26223/5
##### http://www.sthda.com/english/wiki/ggplot2-error-bars-quick-start-guide-r-software-and-data-visualization
##### https://www.r-graph-gallery.com/211-basic-grouped-or-stacked-barplot.html

#### colMeans plot (without sd)
##### K = 2
```{r}
#par(mar) --> sets the margin sizes in the following order: bottom, left, top and right
pdf("hc2_mean.pdf", width = 8, height = 6)
par(oma = c(4, 4, 4, 4), mar=c(3, 2, 2, 10))
barplot(t(mean_df_2), legend.text = TRUE, horiz = TRUE, 
        col = c("#abd9e9", "#d7191c", "#2c7bb6", "#fdae61", "#ffffbf"),
        main = "K = 2: Mean value of subsistence vars. per cluster",
        xpd = TRUE, plot = TRUE,
        args.legend = list(x = 140, y = 1.5, bty = "n", cex = 0.8))
dev.off()
```
##### K = 7
```{r}
pdf("hc7_mean.pdf", width = 8, height = 6)
par(oma = c(4, 4, 4, 4), mar=c(3, 2, 2, 10))
barplot(t(mean_df_7), legend.text = TRUE, horiz = TRUE, 
        col = c("#abd9e9", "#d7191c", "#2c7bb6", "#fdae61", "#ffffbf"),
        main = "K = 7: Mean value of subsistence vars. per cluster",
        xpd = TRUE, plot = TRUE,
        args.legend = list(x = 140, y = 5.5, bty = "n", cex = 0.8))
dev.off()
```

##### K = 15
```{r}
pdf("hc15_mean.pdf", width = 11, height = 9)
par(oma = c(4, 4, 4, 4), mar=c(3, 2, 2, 10))
barplot(t(mean_df_15), legend.text = TRUE, horiz = TRUE, 
        col = c("#abd9e9", "#d7191c", "#2c7bb6", "#fdae61", "#ffffbf"),
        main = "K = 15: Mean value of subsistence vars. per cluster",
        xpd = TRUE, plot = TRUE,
        cex.names = 0.95,
        space = 0.5,
        args.legend = list(x = 127, y = 10.5, bty = "n"))
dev.off()
```

#### To try to include error bars: ggplot
##### The data structure required by ggplot is different
##### Create ggplot_required dataframes for K = 2, 7, 15
##### K = 2
```{r}
require(varhandle)
gg_mean_v_2 <- vector()
gg_sd_v_2 <- vector()
for (i in 1:2){
  gg_mean_v_2 = c(gg_mean_v_2, get(paste0("hc2_colMeans_k_", i)))
  gg_sd_v_2 = c(gg_sd_v_2, get(paste0("hc2_sd_k_", i)))
}
cluster_id_2 = c(rep("c1",length(hc2_colMeans_k_1)), rep("c2", length(hc2_colMeans_k_1)))
variables_2 = rep(names(hc2_colMeans_k_1),2)
gg_mean_df_2 = data.frame(cbind(cluster_id_2, variables_2, gg_mean_v_2))
colnames(gg_mean_df_2) <- c("cluster_id", "subsistence_vars", "value")
rownames(gg_mean_df_2) <- NULL
gg_mean_df_2$value <- unfactor(gg_mean_df_2$value)
```

#### Add error bars to stacked bar plot in ggplot2 - R. To that end it is necessary to compute the y position before plotting: 
```{r}
y_pos_c1 = c(gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Gathering"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Gathering"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Fishing"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Gathering"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Fishing"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c1" & 
                                         gg_mean_df_2$subsistence_vars == "Agriculture"])

y_pos_c2 = c(gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Gathering"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Gathering"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Fishing"],
             gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                       gg_mean_df_2$subsistence_vars == "Husbandry"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Hunting"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Gathering"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Fishing"]+
               gg_mean_df_2$value[gg_mean_df_2$cluster_id == "c2" & 
                                         gg_mean_df_2$subsistence_vars == "Agriculture"])
```

##### Create k2_plot dataset
```{r}
y_pos = c(y_pos_c1, y_pos_c2)
gg_mean_df_2_thursday = cbind(gg_mean_df_2, y_pos, gg_sd_v_2)
```

```{r}
ggplot(data=gg_mean_df_2_thursday, aes(x=cluster_id, y=value, fill=subsistence_vars)) + 
  geom_bar(stat="identity",
       #position="stack",
       width = 0.4) +                           
  xlab(" ") + ylab("Percentage (%)") + 
  theme_classic(base_size = 16) + 
  theme(axis.text.y=element_text(size=16, face="bold")) + 
  theme(axis.title.y=element_text(size=16, face="bold", vjust=1)) + 
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1, size=16, face="bold")) +
  theme(legend.position="right")+
  coord_flip() +
  geom_errorbar(aes(ymax = y_pos + gg_sd_v_2, ymin = y_pos - gg_sd_v_2),
                position = "identity",
                width = 0.1)
```
