---
title: "Sunburst diagrams"
author: "Virginia_Ahedo"
date: "14/10/2020"
output: html_document
---

#### Setup
#### Clean workspace
```{r setup, include=FALSE}
cat("\f")
rm(list=ls(all=TRUE))
knitr::opts_chunk$set(echo = TRUE)
```

#### Set working paths
```{r}
setwd("D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing")
dataPath <- "D:/OneDrive - Universidad de Burgos/Goonies/CULM/GitHub_repository/Lets-go-Fishing"
```

#### Load required libraries
```{r}
require(plotly)
```

### Verification of the precedence relations between the clusters obtained for K = 2, 7, 15.
#### Load Final Clustering results: k = 2, 7, 15.
```{r}
load("hc_2.Rda")
load("hc_7.Rda")
load("hc_15.Rda")
```

#### Subsetting the different clusters
##### K = 2
```{r}
for (i in 1:2){
  assign(paste("hc2_cluster_", i, sep = ""), hc_2[hc_2$hc2.cluster == i,1])
}
```

##### K = 7
```{r}
for (j in 1:7){
  assign(paste("hc7_cluster_", j, sep = ""), hc_7[hc_7$hc7.cluster == j,1])
}
```

##### K = 15
```{r}
for (k in 1:15){
  assign(paste("hc15_cluster_", k, sep = ""), hc_15[hc_15$hc15.cluster == k, 1])
}
```

### Check correspondences
#### Correspondence between clusters hc_2 and hc_7
#### hc2_cluster_1: HGF. 
##### Possible correspondences in hc_7:
##### hc7_cluster_1: HGF - Gatherers
##### hc7_cluster_3: HGF - Hunters
##### hc7_cluster_7: HGF - Fishers
##### Check dimensions:
```{r}
cat("Length of hc2_cluster_1: ", length(hc2_cluster_1))
cat("\nLength of hc7_cluster_1: ", length(hc7_cluster_1))
cat("\nLength of hc7_cluster_3: ", length(hc7_cluster_3))
cat("\nLength of hc7_cluster_7: ", length(hc7_cluster_7))
cat("\nSum of these hc7 subclusters: ", length(hc7_cluster_1)+length(hc7_cluster_3)+length(hc7_cluster_7))
```
##### Second check
```{r}
all(hc7_cluster_1 %in% hc2_cluster_1)
all(hc7_cluster_3 %in% hc2_cluster_1)
all(hc7_cluster_7 %in% hc2_cluster_1)
```
#### hc2_cluster_2: Agriculture & Husbandry.
##### Foreseeable correspondences:
##### hc7_cluster_2: Husbandry
##### hc7_cluster_4: Agriculturalists
##### hc7_cluster_5: AgroFishing
##### hc7_cluster_6: Mixed

#### Check dimensions:
```{r}
cat("Length of hc2_cluster_2: ", length(hc2_cluster_2))
cat("\nLength of hc7_cluster_2: ", length(hc7_cluster_2))
cat("\nLength of hc7_cluster_4: ", length(hc7_cluster_4))
cat("\nLength of hc7_cluster_5: ", length(hc7_cluster_5))
cat("\nLength of hc7_cluster_6: ", length(hc7_cluster_6))
cat("\nSum of these hc7 subclusters: ", length(hc7_cluster_2)+length(hc7_cluster_4)+length(hc7_cluster_5)
    +length(hc7_cluster_6))
```

#### Second check:
```{r}
all(hc7_cluster_3 %in% hc2_cluster_2)
all(hc7_cluster_4 %in% hc2_cluster_2)
all(hc7_cluster_5 %in% hc2_cluster_2)
all(hc7_cluster_6 %in% hc2_cluster_2)
```

#### Correspondence between clusters hc_7 and hc_15
#### hc7_cluster_1: HGF - Gatherers.
##### Possible correspondences in hc_15:
##### hc15_1: HG - Gatherers
##### hc15_2: HFG - Gatherers
##### Check dimensions:
```{r}
cat("Length of hc7_cluster_1: ", length(hc7_cluster_1))
cat("\nLength of hc15_cluster_1: ", length(hc15_cluster_1))
cat("\nLength of hc15_cluster_2: ", length(hc15_cluster_2))
cat("\nSum of the above-mentioned h_15 subclusters: ", length(hc15_cluster_1) + length(hc15_cluster_2))
```

##### Second check:
```{r}
all(hc15_cluster_1 %in% hc7_cluster_1)
all(hc15_cluster_2 %in% hc7_cluster_1)
```

##### hc7_cluster_2: Husbandry.
##### Foreseeable correspondences in hc_15:
##### hc15_3: Husbandry(49%) + Agriculture (22%)
##### hc15_12: Husbandry(75%)

##### Check dimensions:
```{r}
cat("Length of hc7_cluster_2: ", length(hc7_cluster_2))
cat("\nLength of hc15_cluster_3: ", length(hc15_cluster_3))
cat("\nLength of hc15_cluster_12: ", length(hc15_cluster_12))
cat("\nSum of the above-mentioned h_15 subclusters: ", length(hc15_cluster_3) + length(hc15_cluster_12))
```
##### Second check:
```{r}
all(hc15_cluster_3 %in% hc7_cluster_2)
all(hc15_cluster_12 %in% hc7_cluster_2)
```

#### hc7_cluster_3: HGF - Hunters
##### Foreseeable correspondences in hc_15:
##### hc15_4: HGF - Hunters - G(16%)H(70%)F(9%)

##### Check dimensions:
```{r}
cat("Length of hc7_cluster_3: ", length(hc7_cluster_3))
cat("\nLength of hc15_cluster_4: ", length(hc15_cluster_4))
```

##### Second check:
```{r}
all(hc15_cluster_4 %in% hc7_cluster_3)
```

#### hc7_cluster_4: Agriculture(62%) + Husbandry(20%)
##### Possible correspondences:
##### hc15_cluster_5: Agro(63%)pastoralists(22%)
##### hc15_cluster_6: Agriculture(50%) + Husbandry(35%)
##### hc15_cluster_8: Agro(66%)Hunting(12%) + Husbandry(10%)
##### Check dimensions:
```{r}
cat("Length of hc7_cluster_4 ", length(hc7_cluster_4))
cat("\nLength of hc15_cluster_5: ", length(hc15_cluster_5))
cat("\nLength of hc15_cluster_6: ", length(hc15_cluster_6))
cat("\nLength of hc15_cluster_8: ", length(hc15_cluster_8))
cat("\nSum of the above-mentioned h_15 subclusters: ", length(hc15_cluster_5) + length(hc15_cluster_6) + length(hc15_cluster_8)) 
```
##### Second check:
```{r}
all(hc15_cluster_5 %in% hc7_cluster_4)
all(hc15_cluster_6 %in% hc7_cluster_4)
all(hc15_cluster_8 %in% hc7_cluster_4)
```

#### hc7_cluster_5: Agro(51%)Fishing(28%) + Husbandry(10%)
##### Foreseeable correspondences:
##### hc15_cluster_7: Agro(54%)Fishing(20%) + Husbandry(13%)
##### hc15_cluster_9: Agro(47%)Fishing(37%)
##### Check dimensions:
```{r}
cat("Length of hc7_cluster_5: ", length(hc7_cluster_5))
cat("\nLength of hc15_cluster_7: ", length(hc15_cluster_7))
cat("\nLength of hc15_cluster_9: ", length(hc15_cluster_9))
cat("\nSum of the above-mentioned clusters: ", length(hc15_cluster_7) + length(hc15_cluster_9))
```
##### Second check
```{r}
all(hc15_cluster_7 %in% hc7_cluster_5)
all(hc15_cluster_9 %in% hc7_cluster_5)
```

#### hc7_cluster_6: HGF + Agriculture
##### Possible correspondences:
##### hc15_10: Agro(45%)Hunting(28%) + Fishing(18%)
##### hc15_15: HFG + Agriculture

##### Check dimensions:
```{r}
cat("Length of hc7_cluster_6: ", length(hc7_cluster_6))
cat("\nLength of hc15_cluster_10: ", length(hc15_cluster_10))
cat("\nLength of hc15_cluster_15: ", length(hc15_cluster_15))
cat("\nSum of the above-mentioned clusters: ", length(hc15_cluster_10) + length(hc15_cluster_15))
```
##### Second check:
```{r}
all(hc15_cluster_10 %in% hc7_cluster_6)
all(hc15_cluster_15 %in% hc7_cluster_6)
```

#### hc7_cluster_7: HGF - Fishers
##### Foreseeable correspondences:
##### hc15_cluster_11:Fishers
##### hc15_cluster_13: HGF - Fishers
##### hc15_cluster_14: Hunter(39%) - Fishers (48%)

##### Check dimensions:
```{r}
cat("Length of hc7_cluster_7: ", length(hc7_cluster_7))
cat("\nLength of hc15_cluster_11: ", length(hc15_cluster_11))
cat("\nLength of hc15_cluster_13: ", length(hc15_cluster_13))
cat("\nLength of hc15_cluster_14: ", length(hc15_cluster_14))
cat("\nSum of the above-mentioned clusters: ", length(hc15_cluster_11) + length(hc15_cluster_13) + length(hc15_cluster_14))
```
##### Second check:
```{r}
all(hc15_cluster_11 %in% hc7_cluster_7)
all(hc15_cluster_13 %in% hc7_cluster_7)
all(hc15_cluster_14 %in% hc7_cluster_7)
```

### Sunburst diagram
#### With cluster numbers
```{r}
hc2_7_15 <- plot_ly(
  labels = c("hc2_1", "hc2_2",
             "hc7_1", "hc7_2", "hc7_3", "hc7_4", "hc7_5", "hc7_6", "hc7_7",
             "hc15_1", "hc15_2", "hc15_3", "hc15_4", "hc15_5", "hc15_6", "hc15_7", 
             "hc15_8", "hc15_9", "hc15_10", "hc15_11", "hc15_12", "hc15_13", "hc15_14", 
             "hc15_15"),
  parents = c("","",
              "hc2_1", "hc2_2", "hc2_1", "hc2_2", "hc2_2", "hc2_2", "hc2_1",
              "hc7_1", "hc7_1", "hc7_2", "hc7_3", "hc7_4", "hc7_4", "hc7_5", "hc7_4", "hc7_5", "hc7_6",
              "hc7_7", "hc7_2", "hc7_7", "hc7_7", "hc7_6"),
  values = c(275, 1015, 136, 78, 24, 613, 226, 98, 115, 50, 86, 39, 24, 247, 122, 117, 244, 109, 
             49, 15, 39, 68, 32, 49),
  # marker = list(colors = c("#a50026", "#313695", "#d73027", "#f46d43", "#4575b4", "#74add1", 
  #                          "#e0f3f8", "#abd9e9", "#fdae61")),
  marker = list(colors = c("#a50026", "#313695", "#d73027", "#4575b4", "#f46d43", "#74add1", 
                           "#abd9e9", "#e0f3f8", "#fdae61")),
  type = "sunburst",
  branchvalues = "total",
  insidetextorientation='radial',
  width = 700,
  height = 700
)

hc2_7_15
# c("orange","green","sienna1", "tan1", "mediumseagreen", "olivedrab1", "limegreen",
#                            "seagreen", "salmon")
# c("#d73027", "#4575b4", "#f46d43", "#fdae61", "#74add1", "#abd9e9", "#e0f3f8",
#                           "#ffffbf","#fee090")
# c(inlmisc::GetColors(n=24, scheme = "sunset"))
# c("#c51b7d", "#4d9221", "#de77ae", "#f1b6da", "#7fbc41", "#b8e186", "#e6f5d0",
#                            "#f7f7f7", "#fde0ef")
```

#### With cluster description
```{r}
hc2_7_15_desc <- plot_ly(
  labels = c("HGF", "Agriculture & Husbandry",
             "HGF-Gatherers", "Husbandry(62%) + Agric.(17%)", "HGF-Hunters", "Agriculture(62%) + Husb.(20%)",
             "AgroFishing", "HGF + Agriculture", "HGF-Fishers",
             "HG Gatherers - H(32%)G(57%)", "HGF - H(35%)G(37%)F(22%)", "Husb.(49%)Agric.(22%)+H(12%)F(11%)", 
             "Hunters - H(70%)G(16%)F(9%)", "Agro(63%)Pastoralists(22%)", "Agro(50%)Pastoralists(35%)",
             "Agro(54%)Fishing(20%)+Husb.(13%)", "Agro(66%)Hunting(12%)+Husb.(10%)", "Agro(47%)Fishing(37%)+Husb.(7%)",
             "Agro(45%)Hunting(28%)+Fish.(18%)","Fishers - H(14%)F(72%)", "Husbandry(75%) + Agric.(13%)", 
             "HGF-Fishers - H(23%)G(26%)F(45%)", "Hunter-Fishers - H(39%)F(48%)", 
             "H(21%)G(25%)F(15%)+Agric.(35%)"),
  parents = c("","",
              "HGF", "Agriculture & Husbandry", "HGF", "Agriculture & Husbandry", "Agriculture & Husbandry", 
              "Agriculture & Husbandry", "HGF",
              "HGF-Gatherers", "HGF-Gatherers", "Husbandry(62%) + Agric.(17%)", "HGF-Hunters", "Agriculture(62%) + Husb.(20%)", 
              "Agriculture(62%) + Husb.(20%)", "AgroFishing", "Agriculture(62%) + Husb.(20%)", "AgroFishing", 
              "HGF + Agriculture","HGF-Fishers", "Husbandry(62%) + Agric.(17%)", 
              "HGF-Fishers", "HGF-Fishers", "HGF + Agriculture"),
  values = c(275, 1015, 136, 78, 24, 613, 226, 98, 115, 50, 86, 39, 24, 247, 122, 117, 244, 109, 
             49, 15, 39, 68, 32, 49),
  marker = list(colors = c("#a50026", "#313695", "#d73027", "#4575b4", "#f46d43", "#74add1", 
                           "#abd9e9", "#e0f3f8", "#fdae61")),
  type = "sunburst",
  branchvalues = "total",
  insidetextorientation='radial',
  width = 1200,
  height = 1200
)
hc2_7_15_desc
```

##### Another colouring possibility
```{r}
hc2_7_15_desc_2 <- plot_ly(
  labels = c("HGF", "Agriculture & Husbandry",
             "HGF-Gatherers", "Husbandry(62%) + Agric.(17%)", "HGF-Hunters", "Agriculture(62%) + Husb.(20%)",
             "AgroFishing", "HGF + Agriculture", "HGF-Fishers",
             "HG Gatherers - H(32%)G(57%)", "HGF - H(35%)G(37%)F(22%)", "Husb.(49%)Agric.(22%)+H(12%)F(11%)", 
             "Hunters - H(70%)G(16%)F(9%)", "Agro(63%)Pastoralists(22%)", "Agro(50%)Pastoralists(35%)",
             "Agro(54%)Fishing(20%)+Husb.(13%)", "Agro(66%)Hunting(12%)+Husb.(10%)", "Agro(47%)Fishing(37%)+Husb.(7%)",
             "Agro(45%)Hunting(28%)+Fish.(18%)","Fishers - H(14%)F(72%)", "Husbandry(75%) + Agric.(13%)", 
             "HGF-Fishers - H(23%)G(26%)F(45%)", "Hunter-Fishers - H(39%)F(48%)", 
             "H(21%)G(25%)F(15%)+Agric.(35%)"),
  parents = c("","",
              "HGF", "Agriculture & Husbandry", "HGF", "Agriculture & Husbandry", "Agriculture & Husbandry", 
              "Agriculture & Husbandry", "HGF",
              "HGF-Gatherers", "HGF-Gatherers", "Husbandry(62%) + Agric.(17%)", "HGF-Hunters", "Agriculture(62%) + Husb.(20%)", 
              "Agriculture(62%) + Husb.(20%)", "AgroFishing", "Agriculture(62%) + Husb.(20%)", "AgroFishing", 
              "HGF + Agriculture","HGF-Fishers", "Husbandry(62%) + Agric.(17%)", 
              "HGF-Fishers", "HGF-Fishers", "HGF + Agriculture"),
  values = c(275, 1015, 136, 78, 24, 613, 226, 98, 115, 50, 86, 39, 24, 247, 122, 117, 244, 109, 
             49, 15, 39, 68, 32, 49),
  marker = list(colors = c("#8e0152", "#276419", "#c51b7d", "#4d9221", "#de77ae", "#7fbc41", 
                           "#b8e186", "#e6f5d0", "#f1b6da")),
  type = "sunburst",
  branchvalues = "total",
  insidetextorientation='radial',
  width = 1200,
  height = 1200
)
hc2_7_15_desc_2
```

##### Save to pdf
```{r}
orca(hc2_7_15_desc_2, "Sunburst_hc2_7_15_explained.pdf")
orca(hc2_7_15, "Sunburst_hc2_7_15_clust_nb.pdf")
```

